Age-related changes in plant growth and traits

### 2016-12-20 scripts/nutrient.Rmd
adding plots to nutrient analysis showing shifts in bulk stem N & P with shifts in stem diameter. Added temporary diameter column to data - need to instead take mean in R

>>>>

```{r}
stem_segments <- nutrient %>%
    subset(tissue_complete %in% c("wood_from_base","wood_from_middle","wood_from_tip"))%>%
    select(species,age,P,N,diameter_temp,tissue_complete) 
stem_segments$diameter <- as.numeric(stem_segments$diameter)
stem_segments$area <- ((stem_segments$diameter/2)^2)*3.14159

all_species <- unique(stem_segments$species)

pdf("ms/Nutrient/output/stem segment by diameter.pdf", height=11, width=8)
plot

par(mfrow = c(4,2), cex = 1, omi=c(.1,.1,.6,.05), mai=c(1,1,.05,.05))

for (i in seq_along(all_species)) {

data_sp <- filter(stem_segments, species == all_species[i])
plot(P~area,data=data_sp,log="x",col=col.age(data_sp$age),pch=pch.tissue(data_sp$tissue_complete),xlab="",ylab="")
mod <- sma(P~area,data=data_sp,log="x")
mtext("stem area (mm^2)",1,line=1.7,cex=0.7)
mtext("P concentration",2,line=2.3,cex=0.7)
mtext(labels.spp.full(all_species[i]), 3, 0)
plot(N~area,data=data_sp,log="x",col=col.age(data_sp$age),pch=pch.tissue(data_sp$tissue_complete),xlab="",ylab="")
mtext("stem area (mm^2)",1,line=1.7,cex=0.7)
mtext("N concentration",2,line=2.3,cex=0.7)

  if (i %in% c(1,5,9,13)) {
   legend("bottomleft",legend=c("sapwood","wood from mid","wood from base"),pch=c(16,10,7),bty="n",cex=0.8)
   legend("topright",legend=labels.age(),col=col.age(),pch=16, bty="n",cex=0.8)
  }

}

plot(P~diameter,stem_segments,log="xy",col=col.spp(species),pch=16)

stem_segments$diameter <- as.numeric(stem_segments$diameter)
